---
title: 'CJ meta-analysis: factors affecting reliability measures'
author: "George Kinnear"
date: "2022-08-22"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path='figs-web/04-factors-affecting-reliability/')
knitr::opts_chunk$set(dpi=300,fig.width=5)

# for plotting
theme_set(theme_minimal())
#library(patchwork)

library(knitr)
library(kableExtra)
basic_kable = function(df, ...) {
  df %>% 
    kable(...) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)
}
```

# About the sample

```{r}
cj_sessions <- read_csv("data/00-judging_sessions_summary.csv", show_col_types = FALSE)
reliability_stats <- read_csv("data/01-meta-analysis-data.csv", show_col_types = FALSE)

meta_analysis_data <- cj_sessions %>% 
  left_join(reliability_stats, by = "judging_session")

# avoid having to load all the judgement data, by pre-computing the stats in 02-computation.R and loading the results from the 01-meta-analysis-data.csv above.
# source("00-load-all-judgement-data.R")
```

The judging sessions in the sample span a wide range of number of judgements made:

```{r num-judgements}
judgement_data %>% 
  group_by(judging_session) %>% 
  count(name = "num_judgements") %>% 
  mutate(log10_judgements = log(num_judgements, base = 10)) %>% 
  ggplot(aes(x = num_judgements)) +
  geom_histogram(bins = 30) +
  #scale_x_continuous(trans='log10')
  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x),
              labels = scales::trans_format("log10", scales::math_format(10^.x)))
```
There is also a wide range of numbers of items in the different judging sessions - from a handful to a maximum of `r max(meta_analysis_data$observed_N_R, na.rm = TRUE)`.

```{r num-items}
meta_analysis_data %>% 
  filter(observed_N_R > 0) %>% 
  ggplot(aes(x = observed_N_R)) +
  geom_histogram(bins = 30) +
  scale_x_continuous(trans='log10') +
  labs(x = "Number of items being judged")
```

# Proportion of the comparison matrix that is filled

For a judging session with $N$ items, there are $\frac{N(N-1)}{2}$ possible pairs to judge.

Perhaps a factor that influences reliability is how many of these possible pairs are actually considered by judges?

Here we compute the number of possible pairs in each judging session, and compare that with the actual number of pairs that were seen by judges:

```{r}
# TODO - this is computationally a bit heavy, so maybe move it to 02-computation and cache the results

```

There is a bimodal pattern. Most commonly, all (or nearly all) pairs are judged. But another common case is for only around 10% of possible pairs to be judged.

```{r prop-judged}
comparison_matrices %>% 
  select(judging_session, num_pairs, num_pairs_judged, prop_pairs_judged) %>% 
  ggplot(aes(x = prop_pairs_judged)) +
  geom_histogram() +
  labs(x = "Proportion of pairs judged")
```

The proportion of pairs judged does not seem to have a relationship with reliability:

```{r propjudged-vs-splithalves}
meta_analysis_data %>% 
  left_join(comparison_matrices %>% select(judging_session, prop_pairs_judged), by = "judging_session") %>% 
  ggplot(aes(x = prop_pairs_judged, y = mean_split_corr)) +
  geom_hline(yintercept = 0.7, alpha = 0.3, colour = "red") +
  geom_point() +
  geom_smooth(method = "lm", formula = "y ~ x") +
  xlim(c(0,1)) +
  ylim(c(0,1)) +
  labs(x = "Proportion of pairs judged", y = "Mean split-halves correlation")
```

