---
title: "Lens topup"
author: "George Kinnear"
date: "07/06/2021"
always_allow_html: true
output:
  github_document: default
  html_document: default
# knit: (function(inputFile, encoding) {
#   rmarkdown::render(inputFile, encoding = encoding,
#   output_format = "all") })
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)

# Tables
library(knitr)
library(kableExtra)
basic_kable = function(df, ...) {
  df %>% 
    kable(...) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)
}
```

Ben's original Lens.org search was missing various results. This seemed to be due to the way the publication date filter was applied (Ben was specifying year+month+day, while specifying only the year seems pick up more results).

To check what's going on, here we compare:

1. `Original` = Ben's original .bib file, where the year filter was based on the calendar picker ("Date Published = ( 2010-01-01 - 2021-06-01  )")
2. `Topup` = A new version of the .bib file downloaded on 2021-06-07, with the date filter applied as "Year Published = ( 2010 - 2021  )"
3. `Nofilter` = A new version of the .bib file downloaded on 2021-06-07, with no date filter

```{r message=FALSE, warning=FALSE}
original_raw <- bib2df::bib2df("../20210602 CJMetaAnalysis FirstParse.bib")
original <- original_raw %>% janitor::clean_names()
topup_raw <- bib2df::bib2df("ben-search-redone-2021-06-07.bib")
topup <- topup_raw %>% janitor::clean_names()
nofilter <- bib2df::bib2df("ben-search-redone-nofilter-2021-06-07.bib") %>% janitor::clean_names()
```

```{r}
# this version tries to join together keeping the author/year/title, but that causes some mismatches so we don't use this version
comparison_original <- full_join(
    original %>% select(bibtexkey, author, year, title, doi, groups) %>% mutate(source1 = "Original"),
    topup %>% select(bibtexkey, author, year, title, doi) %>% mutate(source2 = "Topup", year = as.character(year)),
    by = c("bibtexkey", "author", "year", "title", "doi")
  ) %>%
  full_join(
    nofilter %>% select(bibtexkey, author, year, title, doi) %>% mutate(source3 = "Nofilter", year = as.character(year)),
    by = c("bibtexkey", "author", "year", "title", "doi")
  )

# instead we join using only the bibtexkey
comparison <- full_join(
    original %>% select(bibtexkey, author, year, title, doi, groups) %>% mutate(source1 = "Original"),
    topup %>% select(bibtexkey, author, year, title, doi) %>% mutate(source2 = "Topup", year = as.character(year)),
    by = c("bibtexkey")
  ) %>%
  full_join(
    nofilter %>% select(bibtexkey, author, year, title, doi) %>% mutate(source3 = "Nofilter", year = as.character(year)),
    by = c("bibtexkey")
  )
```

Curiously there are 160 results from `Original` that are missing from `Topup` (more on that below), but there are about 500 new hits (and about 800 that were date-filtered out in both cases):

```{r}
comparison %>% 
  group_by(source1) %>% 
  count(source2) %>% 
  kable(format = 'markdown')
```

Comparing with the results of the same search with no date filter applied (`Nofilter`):

```{r}
comparison %>% 
  group_by(source1, source2) %>% 
  count(source3) %>% 
  kable(format = 'markdown')
```

The 154 results that appeared in `Original` but not `Topup` are in fact all from before 2010:

```{r}
comparison %>% 
  filter(source1 == "Original", is.na(source2), source3 == "Nofilter") %>% 
  count(year) %>% 
  kable(format = 'markdown')
```

The 6 results that don't show up in `Nofilter` are more troubling - these are sources in the `Original` search that are no longer being returned, making it hard to reproduce our process.

Moreover they include some that were tagged up for inclusion:

```{r}
comparison %>% 
  filter(source1 == "Original", is.na(source2), is.na(source3)) %>% 
  count(groups) %>% 
  kable(format = 'markdown')
```

```{r}
worrying <- comparison %>% 
  filter(source1 == "Original", is.na(source2), is.na(source3)) %>% 
  select(-c(source1:source3))

worrying %>% 
#   rowwise() %>% 
#   mutate(author = str_c(author.x, collapse = ", ")) %>% 
  kable(format = 'markdown')
```

Actually, 2 of them are just JabRef metadata. For the others:

1. appears in the topup as lens.org/127-146-777-695-049
2. appears in the topup as lens.org/018-191-594-451-288
3. doesn't appear, but is not relevant anyway
4. is from 2006 so would be excluded anyway

# Conclusion

The date filter seems to have behaved strangely in the original search, but the new "topup" search fixes this and catches further publications that should be screened for inclusion.

We extract from the `Topup` results only those items that have not yet been screened, and write them to a new .bib file,  `lit-search/2021-06-07-topup.bib`.

```{r}
topup_extras <- comparison %>% 
  filter(source2 == "Topup", is.na(source1))

topup_raw %>% 
  semi_join(topup_extras, by = c("BIBTEXKEY" = "bibtexkey")) %>% 
  bib2df::df2bib(file = "2021-06-07-topup.bib")
```

