---
title: "CJ meta-analysis: reliability check"
author: "George Kinnear"
date: "23/06/2021"
always_allow_html: true
output:
  github_document: default
  html_document: default
# knit: (function(inputFile, encoding) {
#   rmarkdown::render(inputFile, encoding = encoding,
#   output_format = "all") })
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)

# Tables
library(knitr)
library(kableExtra)
basic_kable = function(df, ...) {
  df %>% 
    kable(...) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)
}
```

Ben completed the first pass of categorisation:

```{r message=FALSE, warning=FALSE}
ben_part1 <- bib2df::bib2df("../20210602 CJMetaAnalysis FirstParse.bib") %>% 
  mutate(
    decision = case_when(
      str_detect(GROUPS, "Not") ~ "Exclude",
      str_detect(GROUPS, "Theoretical") ~ "Theoretical",
      str_detect(GROUPS, "Request") ~ "Request data",
      TRUE ~ NA_character_
    )
  )
```

```{r}
ben_part1 %>% 
  select(BIBTEXKEY, decision)  %>% 
  janitor::tabyl(decision) %>% 
  janitor::adorn_totals() %>% 
  select(-valid_percent) %>%
  janitor::adorn_pct_formatting(,,,,"percent") %>% 
  basic_kable()
```

We pick out random sample of 10% of the "Exclude" and "Theoretical" groups for Ian/George to check.

```{r}
set.seed(1)
part1_sample <- ben_part1 %>%
  # remove the NOTE field as that messes up the .bib output
  select(-NOTE) %>% 
  # we'll look at the "request data" ones more closely anyway, so ignore for now
  filter(decision != "Request data") %>% 
  group_by(decision) %>% 
  slice_sample(prop = 0.1) %>% 
  ungroup()

part1_sample %>% 
  group_by(decision) %>% 
  tally() %>% 
  basic_kable()
```

These are divided up evenly between George and Ian, and the entries are written to two new .bib files:

* `2021-06-23-reliability-part1-GK.bib`
* `2021-06-23-reliability-part1-IJ.bib`

```{r}
part1_sample <- part1_sample %>% 
  # give even rows to George, odd rows to Ian
  mutate(reviewer = case_when(
    row_number() %% 2 == 0 ~ "George",
    TRUE ~ "Ian"
  )) %>% 
  # hide the previously-assigned groups
  select(-any_of(c("GROUPS", "decision")))

part1_sample %>% 
  filter(reviewer == "George") %>% 
  select(-reviewer) %>% 
  bib2df::df2bib(file = "2021-06-23-reliability-part1-GK.bib")

part1_sample %>% 
  filter(reviewer == "Ian") %>% 
  select(-reviewer) %>% 
  bib2df::df2bib(file = "2021-06-23-reliability-part1-IJ.bib")
```

## Review process

Setup: 

1. Open the .bib file using JabRef (https://www.jabref.org/).
2. Make sure "View > Groups interface" is turned on. Then in the bottom of the Groups panel, click the "+" icon to add a new group. Type `Agree` for the group name, then click OK. Repeat, to set up another group called "Disagree".

Reviewing:

1. Work your way down the list of articles. There is a column of globe icons, which gives the link for each item - either the DOI (taking you direct to the full text) or the lens.org page (where you can look for details of how to find the article).
2. Review the full text to check if you agree that the article is not within scope.
3. Record your decision by dragging and dropping the item onto the relevant group (Agree = exclude, Disagree = should be included).
4. Save the .bib file!