---
title: "CJ meta-analysis: final screening"
author: "George Kinnear"
date: "07/06/2021"
always_allow_html: true
output:
  github_document: default
  html_document: default
# knit: (function(inputFile, encoding) {
#   rmarkdown::render(inputFile, encoding = encoding,
#   output_format = "all") })
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)

# Tables
library(knitr)
library(kableExtra)
basic_kable = function(df, ...) {
  df %>% 
    kable(...) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)
}
```

Divide up the "request data" group between us.

```{r echo=TRUE}
# TODO: some code to pull out relevant content from the .bib file and produce a spreadsheet
```

## Screening steps

* For each publication, consult the full-text to confirm there is CJ going on.

* If so, record details in the spreadsheet to prepare for the data request emails.

The spreadsheet should look like this:

| Column        | Value       |
| ------------- |-------------|
| publication details | this will be a group of columns, produced automatically in the previous step (lens.org link, authors, year, title, doi) |
| uses_cj | yes/no - does this publication report on CJ data that is within scope? |
| corresponding_author_name | identify the corresponding author (who we will contact about the data request) |
| corresponding_author_email | e-mail address for the corresponding author |
| open_data | link to openly-available data, if it exists (otherwise leave blank) |
| open_data_notes | space for comments about the open data, e.g. "judge IDs seem to be missing" or "looks like lots of filtering is needed" |
| email_notes | if there is no open data, write a snippet that can be used in the data request email to clarify the request, e.g. "decision files for experiment 2" |