---
title: "CJ meta-analysis: final screening"
author: "George Kinnear"
date: "06/07/2021"
always_allow_html: true
output:
  github_document: default
  html_document: default
# knit: (function(inputFile, encoding) {
#   rmarkdown::render(inputFile, encoding = encoding,
#   output_format = "all") })
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)

# Tables
library(knitr)
library(kableExtra)
basic_kable = function(df, ...) {
  df %>% 
    kable(...) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)
}
```

Following the first pass of screening, we have a set of papers that have been tagged as "Request data".

```{r message=FALSE, warning=FALSE}
screened_papers <- bib2df::bib2df("../20210702 CJMetaAnalysis.bib") %>% 
  mutate(
    decision = case_when(
      str_detect(GROUPS, "Not") ~ "Exclude",
      str_detect(GROUPS, "Theoretical") ~ "Theoretical",
      str_detect(GROUPS, "Request") ~ "Request data",
      TRUE ~ NA_character_
    )
  )
```

```{r}
screened_papers %>% 
  select(BIBTEXKEY, decision)  %>% 
  janitor::tabyl(decision) %>% 
  janitor::adorn_totals() %>% 
  select(-valid_percent) %>%
  janitor::adorn_pct_formatting(,,,,"percent") %>% 
  basic_kable()
```

We need to scrutinise these papers more closely for inclusion in the meta-analysis.

```{r}
request_data_papers <- screened_papers %>% 
  filter(decision == "Request data") %>% 
  janitor::clean_names()

request_data_table <- request_data_papers %>% 
  rowwise() %>% 
  transmute(
    bibtexkey,
    author = paste(stringr::word(author, start = -1), collapse = ", "),
    year,
    title,
    doi,
    url,
    category = case_when(str_detect(groups, "Education") ~ "Education", TRUE ~ "Other")
  )

request_data_table %>% 
  janitor::tabyl(category) %>% 
  basic_kable()

request_data_table %>% 
  basic_kable()
```

## Divide up between us

```{r}
set.seed(12345)

allocation <- request_data_table %>% 
  mutate(
    assigned_to = case_when(
      str_detect(author, "Bartholomew|Seery") ~ "George",
      str_detect(author, "Davies|Verhavert|Lesterhuis|Goossens|Roose|Coertjens") ~ "Ben",
      str_detect(author, "Jones|Alcock|Inglis|Barmby|Benton|Wheadon|Bramley|Pollitt") ~ "Ian",
      # these authors each have 2-3 papers
      str_detect(author, "Attali|Barber|Newhouse|Tarricone") ~ "George",
      TRUE ~ sample(c("Ben", "Ian", "George"), 1)
    )
  )

allocation %>%
  janitor::tabyl(assigned_to, category) %>%
  left_join(
    allocation %>%
      janitor::tabyl(assigned_to),
    by = "assigned_to") %>%
  basic_kable()

# allocation %>% 
#   filter(is.na(assigned_to)) %>% 
#   select(author) %>% 
#   mutate(author = str_split(author, pattern = " ")) %>% 
#   unnest(author) %>% 
#   janitor::tabyl(author) %>% 
#   arrange(-n) %>% 
#   basic_kable()

```

```{r eval=FALSE, include=FALSE}
# this chunk is set to eval=FALSE now so that we don't overwrite the spreadsheet!
allocation %>% 
  mutate(uses_cj = "",
         corresponding_author_name = "",
         corresponding_author_email = "",
         open_data = "",
         open_data_notes = "",
         email_notes = "") %>% 
  arrange(assigned_to, category, author, year) %>% 
  writexl::write_xlsx("2021-06-07-final-screening-blank.xlsx")
```


## Screening steps

* For each publication, consult the full-text to confirm there is CJ going on.

* If so, record details in the spreadsheet to prepare for the data request emails.

The spreadsheet should look like this:

| Column        | Value       |
| ------------- |-------------|
| publication details | this will be a group of columns, produced automatically in the previous step (lens.org link, authors, year, title, doi) |
| uses_cj | yes/no - does this publication report on CJ data that is within scope? |
| corresponding_author_name | identify the corresponding author (who we will contact about the data request) |
| corresponding_author_email | e-mail address for the corresponding author |
| open_data | link to openly-available data, if it exists (otherwise leave blank) |
| open_data_notes | space for comments about the open data, e.g. "judge IDs seem to be missing" or "looks like lots of filtering is needed" |
| email_notes | if there is no open data, write a snippet that can be used in the data request email to clarify the request, e.g. "decision files for experiment 2" |