---
title: "Lens topup search in 2024"
author: "George Kinnear"
date: "2024-04-11"
always_allow_html: true
output:
  github_document: default
  html_document: default
# knit: (function(inputFile, encoding) {
#   rmarkdown::render(inputFile, encoding = encoding,
#   output_format = "all") })
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)

# Tables
library(knitr)
library(kableExtra)
basic_kable = function(df, ...) {
  df %>% 
    kable(...) %>%
    kable_styling(bootstrap_options = "striped", full_width = F)
}
```

## Repeated search

> (
>  ("comparative judgement" OR "comparative judgment")
>  OR
>  (("pairwise comparisons" OR "paired comparisons") AND "Bradley" AND "Terry")
> )

We repeated the lens.org search on 11/04/2024, with the "Year Published" filter set to "2021 - " (since the previous search had included all sources "2010 - 2021" but was run mid-way through 2021).

```{r message=FALSE, warning=FALSE}
new_results <- bib2df::bib2df("lens-export-2024-04-11.bib") %>% janitor::clean_names()
```

This new search returned `r nrow(new_results)` hits.

There is a little bit of overlap with the previous search, though.

```{r message=FALSE, warning=FALSE}
original <- bib2df::bib2df("../20210602 CJMetaAnalysis FirstParse.bib") %>% janitor::clean_names()

previous_topup <- bib2df::bib2df("2021-06-07-topup.bib") %>% janitor::clean_names()
```
```{r}
genuine_new_hits <- new_results %>% 
  anti_join(original, join_by(bibtexkey)) %>% 
  anti_join(previous_topup, join_by(bibtexkey))
```

That still leaves `r nrow(genuine_new_hits)` genuinely new records to review.

This does include some new work that is definitely in scope for us:

```{r}
genuine_new_hits %>% 
  filter(str_detect(author, "Inglis")) %>% 
  select(bibtexkey, author, year, title, doi) %>% 
  basic_kable()
```



